---
title: Calendar
author: Ben Harden
date: '2021-05-20'
slug: []
categories: []
tags: []
draft: no
---

Class period will be 12pm to 3pm daily (Eastern time). During this time you can expect the following structure

```{r, echo = FALSE}
knitr::kable(
  tibble::tribble(~"Time", ~"Activity",
                  "11:30", "Submit daily check-in survey",
                  "12:00 - 12:30", "Whole group check-in",
                  "12:30 - 2:00","Work block",
                  "2:00 - 3:00","Whole group activity"))
```

There will be a super quick daily survey to fill in to let us know how you're getting on and what you might need help with. Please fill this out by 11:30am Eastern (or the evening before if you are on Pacific Time).

The initial check in will be to see how folks are getting on, gather thoughts for what assistance people need, and possible play some review games.

The work block is time for students to work independently or in groups on their level work. This is also the time instructors will be helping people in one-on-one or small group discussions.

The daily 2pm-3pm window will be used for synchronous interactions. These will be posted to the PEP 2021 Google Calendar, but the following is a provisional list of topics.

```{r, echo = F}
knitr::kable(
  tibble::tribble(~"Date         ", ~"Topic",~"Notes",
                  "June 3", "Practice Discussion (Intro to R: Level 2)","Small group discussions",
                  "June 4", "Temperature, Salinity and Density: Level 3","Small group discussions (scored)",
                  "June 7", "Phytoplankton and Nutrients: Level 3", "Small group discussions (scored)",
                  "June 8", "Carbon and Oxygen: Level 3", "Small group discussions (scored)",
                  "June 9", "Reading a Paper: Level 3", "Small group discussions (scored)",
                  "June 10", "A Changing Ocean: Level 3", "Small group discussions (scored)",
                  "June 11", "Advanced topic #1", "Guest Speaker",
                  "June 14", "No scheduled activity", "NA",
                  "June 15", "Literature Review: Level 2", "Small group presentations (scored): 12:30pm-1:30pm",
                  "June 15", "Advanced topic #2", "Guest Speaker",
                  "June 16", "Advanced topic #3", "Guest Speaker",
                  "June 17", "Advanced topic #4", "Guest Speaker",
                  "June 18", "Juneteenth Holiday: No class", "",
                  "June 21", "Scientific Poster: Level 2", "Class discussion: 12pm - 1pm",
                  "June 21", "Data Discovery: Level 3", "Small group presentations (scored)",
                  "June 22", "Advanced topic #4", "Guest Speaker",
                  "June 23", "Team check-ins", "",
                  "June 24", "Team check-ins", "",
                  "June 25", "Scientific Poster: Level 3", "Poster presentation session (scored)",
                  "June 28", "Scientific Talk: Level 3", "Individual talks (scored)"
                  )
)
```